Response to the defense feedback

### 2021-06-18 Chapter-7/Chapter-7.tex
Updates from Overleaf

In conclusion, this dissertation research develops practical techniques for precise side-channel analysis in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effeteness and generality of our proposed method.  We also release the prototypes to facilitate future research in the area.
\section{Future Directions}
There are a few potential directions the dissertation research.

@@

>>>>

In conclusion, this dissertation research develops practical techniques for precise side-channel analysis in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effeteness and generality of our proposed method.  We also release the prototypes to facilitate future research in the area.
\section{Future Directions}
There are a few potential directions to extend the dissertation research.

@@

\textbf{Side-channel Leakage Quantification with A Noisy Observation.}It is possible to extend the quantification part to include other side-channel
signals (e.g., sound, CPU usages, EM signals). The key is to model the noises
properly. In my dissertation, we assume that an attacker can have a noise-free
observation. While a noise-free observation is possible for some address-based
side-channel attacks, the assumption is too ideal for many real side-channel
attacks. The good news is that there are some mature methods in information theory to model noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a
computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations.
